Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-04-25 tese/section03.tex
organized some bibliography

  \ac{CSS} idea is to separate the structure of an \ac{XML} document from its appearance. \ac{CSS} defines styles for \ac{XML} tags based on their name, class or identifier, besides static styling it supports animations and transitions leading to a more dynamic content.

  \textit{Javascript} is an imperative object oriented language based on ECMAScript. It is used mainly on client-side and executed by a web browser. Javascript has it own implementation of \ac{DOM} and one of its advantages is the ability to download and execute code on the fly without the need of a pre-installed plugin.

>>>>

  \ac{CSS} idea is to separate the structure of an \ac{XML} document from its appearance. \ac{CSS} defines styles for \ac{XML} tags based on their name, class, identifier or position, besides static styling it also supports animations and transitions leading to a more dynamic content.

  \textit{Javascript} is an imperative object oriented language based on ECMAScript. It is used mainly on client-side and executed by a web browser. Javascript has it own implementation of \ac{DOM} and one of its advantages is the ability to download and execute code on the fly without the need of pre-installed plugins.
